Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
quantify dev team and code review

Started in 2009, \sklearn is developed by a large and
international team of volunteers, mostly researchers from
various fields (e.g., machine learning, natural language processing, or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features. Finally, any addition to the code base goes through rigorous
code review.

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications of a previous paper
\citep{pedregosa2011}, successes in various machine learning challenges
(\emph{e.g.} kaggle), or significant statistics derived from our repositories
and mailing lists.  At the time of writing, the project is watched by 1309
people and forked 667 time on github, and the mailing-list receives 300 mails
per month.

@@

% The scikit-learn project started in 2009 and has since been developed
% by a team largely consisting of scientists
% (both from computer science and other fields).
% Its popularity can be gauged from various sources:
% % TODO: list volume on the mailing list, number of contributors,
% % number of issues opened and closed, number of forks, number of surveys filled in.
% at the time of writing,
% the popular programmer's Q~\&{}A site StackOverflow\footnote{
%   \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% % update the following figure when paper is finalized
% lists 322 scikit-learn-related questions.
% The version control logs for the development version of scikit-learn
% % ddaa494c116e3c16bf032003c5cccbed851733d2
% show 183 contributors to the project's source code and documentation
% (after manual deduplication).

>>>>

Started in 2009, \sklearn is developed by an international team
of several dozen volunteers, mostly researchers from various fields
(e.g., machine learning, natural language processing, or neuroscience).
The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features.
Finally, additions to the code base must pass code review
by at least two developers not involved in the implementation
of the proposed addition.

Within the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications of a previous paper
\citep{pedregosa2011}, successes in various machine learning challenges
(\emph{e.g.} kaggle), or significant statistics derived from our repositories
and mailing lists.  At the time of writing, the project is watched by 1309
people and forked 667 time on GitHub, and the mailing-list receives 300 mails
per month.
The version control logs for the development version of scikit-learn
% ddaa494c116e3c16bf032003c5cccbed851733d2
show 183 contributors to the project's source code and documentation
(after manual deduplication).

@@

% The scikit-learn project started in 2009 and has since been developed
% by a team largely consisting of scientists
% (both from computer science and other fields).
% Its popularity can be gauged from various sources:
% % TODO: list volume on the mailing list, number of contributors,
% % number of issues opened and closed, number of forks, number of surveys filled in.
% at the time of writing,
% the popular programmer's Q~\&{}A site StackOverflow\footnote{
%   \url{http://stackoverflow.com/questions/tagged/scikit-learn}}
% % update the following figure when paper is finalized
% lists 322 scikit-learn-related questions.
